Meeting the Challenges of Modeling Astrophysical Thermonuclear Explosions: \castro, \maestro, and the \amrex\ Astrophysics Suite

### 2017-10-24 astronum_2017/astronum-amrex.tex
removed mention of weak scaling as we never show any of these results

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{sedov_scaling}
\includegraphics[width=0.48\linewidth]{wdmerger_scaling}
\caption{\label{fig:castro-scaling} (left) \castro\ strong scaling on
  OLCF Titan for a pure hydro (Sedov w/ real EOS) problem.  The
  different colors represent different base resolutions.  We see
  excellent strong and weak scaling for the single level runs.  For
  the $1024^3$ run, we also ran with one level of refinement by a
  factor of 2 (triangles) or a factor of 4 (squares), and see good
  strong scaling.  The variability (shown by the error bars) at high
  core counts shows we are becoming work-starved. (right)
  \castro\ strong scaling on OLCF Titan for a hydro + Poisson gravity
  (wdmerger) problem.  This problem uses a multipole solver to
  determine Dirichlet boundary conditions representing an isolated
  mass distribution, and then geometric multigrid to solve for the
  potential in the interior.  Two coarse grid sizes are shown, and
  demonstrate great strong scaling.  We also look at a single level of
  refinement (by a factor of 4) on top of this coarse grid.}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.48\linewidth]{sedov_scaling}
\includegraphics[width=0.48\linewidth]{wdmerger_scaling}
\caption{\label{fig:castro-scaling} (left) \castro\ strong scaling on
  OLCF Titan for a pure hydro (Sedov w/ real EOS) problem.  The
  different colors represent different base resolutions.  We see
  excellent strong scaling for the single level runs.  For the
  $1024^3$ run, we also ran with one level of refinement by a factor
  of 2 (triangles) or a factor of 4 (squares), and see good strong
  scaling.  The variability (shown by the error bars) at high core
  counts shows we are becoming work-starved. (right) \castro\ strong
  scaling on OLCF Titan for a hydro + Poisson gravity (wdmerger)
  problem.  This problem uses a multipole solver to determine
  Dirichlet boundary conditions representing an isolated mass
  distribution, and then geometric multigrid to solve for the
  potential in the interior.  Two coarse grid sizes are shown, and
  demonstrate great strong scaling.  We also look at a single level of
  refinement (by a factor of 4) on top of this coarse grid.}
\end{figure}
